Parsing Tweets into Universal Dependencies

### 2017-12-01 paper.tex
finish section 2

\paragraph{Vocative at-mentions.}  Another idiomatic construction on
Twitter is an at-mention %(followed by a colon \nascomment{?})
as a sign that a tweet is a reply to a tweet by the mentioned user\yicomment{not necessary, can be just mentioning somebody. should be careful to say it. We can say this construction include 1. reply;  2. mention sb. Both cases are similar to general vocative proper noun case in standard texts}.  We
treat these at-mentions as vocative expressions, labeling them as
\emph{proper noun} (\texttt{PROPN})[YI COMMENT: here is confusing that PROPN could be a label in dependencies. We can say in POS sections that the decisions on some twitter specific tokens can be made only analyzing syntax together.] and attaching them to the
following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example) \yicomment{just as UD guidelines}.

@@

\subsection{\sc Tweebank v2}\label{sec:anno-process}
Following the guidelines presented above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.

@@

\subsubsection{Annotation Process}
Our annotation process was conducted in three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the UD
annotation conventions and our guidelines.
Both the guidelines and annotations
were further refined by the authors of this paper to increase
the coverage of our guidelines and solve inconsistencies between
different annotators during this exercise. In the second stage, a POS tagger and
parser were trained on the annotated data from the first stage (1,041 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data. Finally, an extra
layer of word-level normalization was manually annotated for data
analysis purposes.

@@

We report the inter-annotator agreement between the annotators
in the second stage. The agreement on POS is 96.6\%, the unlabeled
dependency agreement is 88.8\% and the labeled dependency agreement
is 84.3\%. Further analysis shows the major disagreements on POS
involve entity names (30.6\%) and topical hashtags (18.1\%).
Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' can
be understood as a verbal phrase but also as the name of the Coldplay's
single and tagged as proper noun. An example of a disagreement on
dependencies is shown in Figure \ref{fig:disagree}.  Depending on
whether this is an example of an empty auxiliary verb, or a clause-modified
noun, either annotation is plausible.

>>>>

\paragraph{Vocative at-mentions.}  Another idiomatic construction on
Twitter is an at-mention %(followed by a colon \nascomment{?})
as a sign that a tweet is a reply to a tweet by the mentioned user\yicomment{not necessary, can be just mentioning somebody. should be careful to say it. We can say this construction include 1. reply;  2. mention sb. Both cases are similar to general vocative proper noun case in standard texts}.  We
treat these at-mentions as vocative expressions, labeling them as
\emph{proper noun} (\texttt{PROPN})\yicomment{here is confusing that PROPN could be a label in dependencies. We can say in POS sections that the decisions on some twitter specific tokens can be made only analyzing syntax together.} and attaching them to the
following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example) \yicomment{just as UD guidelines}.

@@

\subsection{\sc Tweebank v2}\label{sec:anno-process}
Following the guidelines presented above, we create a new annotated\yicomment{del?} Twitter \yicomment{Twitter dependency} treebank, which we call {\sc Tweebank v2}.

@@

\subsubsection{Annotation Process}
Our annotation process was conducted in three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the \yicomment{general} UD
annotation conventions and our guidelines \yicomment{specifically for annotating tweets}.
Both the guidelines and annotations
were further refined by the authors of this paper to increase
the coverage of our guidelines and solve inconsistencies between
different annotators during this exercise. In the second stage, a POS tagger and
parser were trained on the annotated data from the first stage (1,050\yicomment{changed to 1050} tweets in total),
and \yicomment{were?}used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data. Finally, an extra
layer of word-level normalization\yicomment{see 10 th col of conllu data, also mention we could recover the original tweets also from this col (tokenization)} was manually annotated for data
analysis purposes.\yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them. Good story :)}

@@

We report the inter-annotator agreement between the annotators
in the second stage\yicomment{tokenization is easier, did not do inter-annotator agreement}. The agreement on POS is 96.6\%, the unlabeled
dependency agreement is 88.8\% and the labeled dependency agreement
is 84.3\%. Further analysis shows the major disagreements on POS
involve entity names (30.6\%) \yicomment{noun phrases or proper noun phrases, do we need example here?} and topical hashtags (18.1\%).
Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' \yicomment{need to relate to previous error analysis, entity names maybe?}can
be understood as a verbal phrase but also as the name of the Coldplay's
single and tagged as proper noun. \yicomment{need to say the reason why dependency inter-annotator agreement is low? 1. POS disagreement lead to big difference in understanding the semantics. 2. Some special constructions like ellipsis lead to different view of tweets. Fig3 is an example of 2.}An example of a disagreement on
dependencies is shown in Figure \ref{fig:disagree}.  Depending on
whether this is an example of an empty auxiliary verb, or a clause-modified
noun, either annotation is plausible.
